\newpage
\section{Introduction}
CAEN provides several softwares that a digitizer can run for data acquisition: DPP-CI
(now deprecated), DPP-PSD, CAENScope, \href{https://www.caen.it/products/caen-wavedump/}{WaveDump} (https://www.caen.it/products/caen-wavedump/) (hereinafter the \blt{WD}), etc. The
software described in this document is designed to work with the data acquired with
\blt{WD} software. \blt{WD} allows user to save the acquired data in two formats: either
binary or ASCII. Since saving data in binary format provides higher record rate and
more information about the data, and takes less space on disk, one should choose it in
order to get better performance in case when analysis of large number of events is 
needed (for example, to get integral spectrum or average waveform).

However, parsing of binary files requires a bit more complicated algorithms comparing with those needed in 
case of using ASCII files. So this software is intended to provide a simple C++ interface
to work with \blt{WD}'s binary data files. Moreover, this software can be easily ''extended''
by user in the following sense. Each event consisting of data points (or a waveform) and 
some additional info is represented by and accessible through the \codet{Event} class (described below).
This allows user to write his/her own functions to perform any kind of analysis on an event
using only \codet{Event} object which stores given event.

\Warning{This software is NOT considered to work with ASCII files. So use it only
with binaries produced by the \blt{WD} software.}

Operating CAEN digitizer with \blt{WD} software for data acqusition requires a
configuration file containing device settings. This file is just a text file which
(mostly) consists of lines like this 

\begin{lstlisting}
<parameter> <value>
\end{lstlisting}
that define digitizer's behavior.

Of course, it is possible to create such file directly using a text editor just once
and any time another configuration is needed just copy and change it. However, it would be
a bit more convenient to have a tool that constructs configuration file automatically.
